\sout{A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network} \rev{A routing protocol for an urban IoT based on a smart street lighting wireless sensor network}

### 2014-12-19 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
todas as repostas completadas.

Due to these not negligible drawbacks, it is wise to develop some work around able to improve the RPL protocol deficiencies, mainly that related with P2P messages. One of the possible approaches is the use of geographic routing techniques, which are routing algorithms known by its low overhead and high scalability features \citep{Karp_GPSR_2000, Position_Based_Routing_Ad_Hoc_2001, On_Optimal_Geographic_Routing_2007}.

>>>>

Due to these not negligible drawbacks, it is wise to develop some work around able to improve the RPL protocol deficiencies, mainly that related with P2P messages. \rev{To this end, a reactive distance vector routing protocol called LOADng (Lightweight Ad hoc On-Demand - Next Generation (LOADng)) has been proposed \citep{LOADng_2012}. However, in recently published papers (\citep{Tripathi2014, Vucinic_2013}, LOADng was compared to RPL  and, according to the authors, LOADng may even have worse performance than RPL according to several metrics, including average delay, control overhead and maximum memory requirements. Therefore, in this paper, we follow another possible approach for routing. Such approach} \sout{One of the possible approaches} is the use of geographic routing techniques, which are routing algorithms known by its low overhead and high scalability features \citep{Karp_GPSR_2000, Position_Based_Routing_Ad_Hoc_2001, On_Optimal_Geographic_Routing_2007}.
